Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-21 paper/paper.tex
another pass

%% \author{
%% \IEEEauthorblockN{Sabrina Souto}
%% \IEEEauthorblockA{State University of Para\'iba\\
%% Para\'iba, Brazil\\
%% sabrinadfs@gmail.com}
%% \and
%% \IEEEauthorblockN{Marcelo d'Amorim}
%% \IEEEauthorblockA{Federal University of Pernambuco\\
%%   Pernambuco, Brazil\\
%%   damorim@cin.ufpe.br}
%% \and
%% \IEEEauthorblockN{Rohit Gheyi}
%% \IEEEauthorblockA{Federal University of Campina Grande\\
%%   Para\'iba, Brazil\\
%%   rohit@dsc.ufcg.edu.br}
%% }

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity. We organized our study in three
parts. First, we report on the stability of the engines we analyzed
using the official Test262 conformance test suite for
EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. Second, we report results
obtained with test transplantation
(Section~\ref{sec:transplantation}). The rationale is that the domain
of possible inputs is too large; consequently, we expect that test
suites written for a given engine cover scenarios and corner cases
uncovered by another engine. To sum, we conjecture that test cases
written for one engine could reveal bugs in different engines as
opposed to only manifesting false alarms. Third, we analyzed the
impact of using cross-engine differential testing to find bugs
(Section~\ref{sec:cross-engine-diff-testing-results}). The rationale
is that black-box fuzzers could expose important bugs.

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows a
summary of the bugs we reported. The figure shows the distribution of
status of bug reports per engine. Note that several of these reports
were not reviewed yet, \ie, they did not receive a label ``confirmed''
or ``rejected'' from the development team. Note also that we did not
find bugs in the Mozilla \smonkey\ engine and that several of the bugs
we reported were already fixed and incorporated to the latest release
of corresponding engines.

@@

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ standard. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. It is important to note that failures are
expected as it takes time for engines to adjust to the
spec.\Mar{...mention the variance was negligible...} We noticed that
all four engines we analyzed but \chakra{} use some variant of the
Test262 suite as part of their regression process, but we used the
same version in this experiment, the one available from the Test262
web site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \jsc\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this test suite indicates missing features
as opposed to bugs. However, note that \chakra\ is both the engine
that has the lowest passing ratio in the conformance test suite and
the one we were able to find more confirmed bugs (as per
Figure~\ref{fig:summary}). We conjecture that the development age of
the engine--Chakra is the newest engine\Fix{find DOB of
  Chakra}--justify both observations.

@@

\Mar{remember to say that we use dataset Table II''compile-in-all''.}

This section reports the results of test transplantation, \ie{}, we
analyzed the failures observed when running a test suite on an engine
other than the engine where the test suite
originated.

Table~\ref{tab:cross-testing} shows the number of failures for each
pair of test suite and engine. The first column shows the test suites
and the first row shows the engines that run those tests. We use a
dash (``-'') to indicate that we did not consider the combinations
that associated a test suite with its parent engine; failures in those
cases would either indicate regressions or flaky tests as opposed to
an unknown bug for that engine. We did not run the test cases that
fail on its parent engine in any other engines; we wanted all tests to
pass on their parent engine as a failure in that case would be a
stronger indicative of a bug. In total, 64 test cases were discarded
for that reason--6 from \jsc{} and 57 from \smonkey. In total, 7,029
test files (\ie{}, 38369-31276-64) were considered in this experiment,
which involved 24,922 test runs (\ie, (7029*4)-1021-57-2116).  Of
these, 812 failures were observed (3.25\% of the runs) across
\textbf{543} distinct files (7.72\% of the files). We analyzed each of
these file in separate to identify if the failure was fault-revealing
or a false positive.

>>>>

\author{
\IEEEauthorblockN{Igor Sim\~oes\qquad{}Marcelo d'Amorim}
\IEEEauthorblockA{Federla University of Pernambuco, Brazil\\
\{isol2,damorim\}@cin.ufpe.br}
}

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity. We organized our study in three
parts. First, we report on the conformance of the engines we analyzed
using the official Test262 conformance test suite for
EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). In the limit, bugs would have low
relevance if the engines are too unreliable. Second, we report results
obtained with test transplantation
(Section~\ref{sec:transplantation}). The rationale is that the domain
of possible inputs is too large; consequently, we expect that test
suites written for a given engine cover scenarios and corner cases
uncovered by another engine.\Comment{ To sum, we conjecture that test
  cases written for one engine could reveal bugs in different engines
  as opposed to only manifesting false alarms.} Third, we analyzed the
impact of using cross-engine differential testing to find bugs
(Section~\ref{sec:cross-engine-diff-testing-results}). Differential
testing has been used in several contexts to address the oracle
problem~\cite{barr-etal-tse2015}. Intuitively, using differential
testing to find functional bugs across engine implementation could be
promising.

\vspace{1ex}
\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows a
summary of the bugs we reported. The figure shows the distribution of
status of bug reports per engine. Note that several of these reports
hold the status ``new'', which indicates that they were not reviewed
yet by the development team. Note also that we did not find bugs in
the Mozilla \smonkey\ engine and that several of the bugs we reported
were already fixed and incorporated in the latest release of
corresponding engines. Overall, discarding bug report with the ``new''
label, we reported \noBugsTotalConfirmed{} bugs.

@@

%% It is important to note that failures are
%% expected as it takes time for engines to adjust to the
%% spec.

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in Test262 (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not expect causality. We
conjecture that the development age of the engine--Chakra is the
newest engine\Fix{find DOB of Chakra}--justify the incidental
correlation.

@@

This section reports results of test transplantation. We analyzed the
failures observed when running a test suite original from a given
engine in another engine. Intuitively, we want to assess how promising
is to use knowledge of developers of a given engine to find bugs in a
different engine.

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. We did not run test
cases that fail on its parent engine in any other engines; we wanted
all tests to pass on their parent engine as that would indicate that
the test case is coherent and can be used. In total, 64 test cases
were discarded for that reason--6 from \jsc{} and 57 from
\smonkey. Furthermore, we required that a test does not manifest
compile errors as we want to focus on bugs in code not in tests. For
that reason, we used the tests listed under the column
``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
  ``compile-in-all'' and not ``origina'' as these numbers
  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
  were considered in this experiment, which involved 24,922 test runs
  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were observed
(3.25\% of the runs) across \textbf{543} distinct files (7.72\% of the
files). We analyzed each of these files in separate as to classify if
the failure was fault-revealing or a false positive.

\Mar{-------------------- estou aqui}
